### 2017-09-27 TF-vldb2018/sec-expt.tex

\ni (3) We also used real-life data \youtube~\cite{youtubeWeb} (see Appendix).

@@

\sstab(2) Our batch algorithm for  top-$k$ team formation is efficient,
\eg it took 110s when $|V|=1.39M$ and $|V_P|=10$.

\sstab (3) Our incremental algorithm for dynamic top-$k$ team formation is able to process continuous pattern and data updates, separately and simultaneously,
and it is more promising than its batch counterpart,
even (a) when changes are 34\% for pattern updates, 31\% for data updates, and (25\%, 22\%) for simultaneous pattern and data updates on average,
and (b) when 29\% for continuous pattern updates, 26\% for continuous data updates and (20\%, 18\%) for continuously simultaneous pattern and data updates on average.

>>>>

\ni (3) We also used real-life dataset \youtube~\cite{youtubeWeb} (see~\cite{fullvldb18}).

@@

\sstab(2) Our batch algorithm for  top-$k$ team formation is efficient,
\eg it took 116s when $|V|=1.39M$ and $|V_P|=10$.

\sstab (3) Our incremental algorithm for dynamic top-$k$ team formation is able to process continuous pattern and data updates, separately and simultaneously,
and it is more promising than its batch counterpart,
even (a) when changes are 36\% for pattern updates, 34\% for data updates, and (25\%, 22\%) for simultaneous pattern and data updates on average,
and (b) when 29\% for continuous pattern updates, 26\% for continuous data updates and (20\%, 18\%) for continuously simultaneous pattern and data updates on average.

### 2017-09-27 TF-vldb2018/sec-intro.tex

\stab (3) Using real-life data (\citationd) and synthetic data (\synthetic), we demonstrate the effectiveness and efficiency of our graph pattern matching approach for (dynamic) team formation (Section~\ref{sec-expt}).
We find that (a) our method is able to identify more sensible teams than existing team formation methods \wrt \eat{three} practical measurements,
and (b) our incremental algorithm outperforms our batch algorithm, even when changes reach 34\% for pattern updates, 31\% for data updates and (25\%, 22\%) for simultaneous pattern and data updates, and when 29\% for continuous pattern updates, 26\% for continuous data updates and (20\%, 18\%) for continuous simultaneous pattern and data updates, respectively.

All detailed proofs are available  in the Appendix.

>>>>

\stab (3) Using real-life data (\citationd) and synthetic data (\synthetic), we demonstrate the effectiveness and efficiency of our graph pattern matching approach for (dynamic) team formation (Section~\ref{sec-expt}).
We find that (a) our method is able to identify more sensible teams than existing team formation methods \wrt \eat{three} practical measurements,
and (b) our incremental algorithm outperforms our batch algorithm, even when changes reach 36\% for pattern updates, 34\% for data updates and (25\%, 22\%) for simultaneous pattern and data updates, and when 29\% for continuous pattern updates, 26\% for continuous data updates and (20\%, 18\%) for continuous simultaneous pattern and data updates, respectively.

All detailed proofs are available  in the full version~\cite{fullvldb18}.
